Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-21 docs/manuscript/manuscript.tex
MICS -> MIS.

\subsection*{Preamble}
We analyzed data from the Demographic Health Survey (DHS) and the Multiple Indicator Cluster Survey (MICS) (1990-2020) to highlight water accessibility predictors in 78 countries throughout the world.

>>>>

\subsection*{Preamble}
We analyzed data from the Demographic Health Survey (DHS) and the Malaria Indicator Survey (MIS) (1990-2020) to highlight water accessibility predictors in 78 countries throughout the world.
